### 2014-06-19 ms/ms.Rmd
In Ms change 'dataset' to 'studyName'

We (D. Falster and R. Duursma, with the help of D. Barneche, R. FitzJohn and A. Vårhammer) set out to create such a resource, by asking authors directly whether they would be willing to make their raw data files freely available. The response was overwhelming: nearly everyone we contacted was interested to contribute their raw data. Moreover, we were invited to incorporate another compilation led by M. Ishihara and focussing on Japanese literature. As a result, we present BAAD: a Biomass And Allometry Database for woody plants, comprising data collected in `r length(unique(data$dataset))` different published and unpublished studies.

@@

**2. Abstract**: Understanding how different plants are plant constructed -- i.e. how key size dimensions and the amount of mass invested in different tissues varies among individuals -- is essential for modelling plant growth, estimating carbon stocks, and mapping the flow of energy in the terrestrial biosphere. Allocation patterns can differ widely through ontogeny, but also among coexisting species, and among species adapted to or grown in different environments. While a variety of models dealing with allocation exist, a synthetic understanding about plant allocation is lacking. This is partly due to the lack of suitable datasets for validating and parametrising models. To that end, we present the Biomass And Allometry Database (BAAD) for woody plants. BAAD contains `r sum(!is.na(data[,vars]))` measurements collected in `r length(unique(data$dataset))` different studies, from `r nrow(data)` individuals across `r length(unique(data$species))` species. Most of this data is associated with an existing publication, however, mostly raw data files were not released at time of publication. Thus BAAD contains individual level data from different studies, transformed into standard units and variable names. The transformations were achieved using a new R package dataMashR.  Other features which distinguish BAAD are that we focussed on studies where: i) measurements were for individual plants rather than stand averages; ii) individuals spanning a range of sizes were measured; iii) inclusion of plants from 0.01-100m in height; and iii) biomass was estimated directly, i.e. not indirectly via allometric equations (with one exception for trees > 60m). We included both wild and artificially grown plants. The dataset contains the following size metrics: total leaf area; area of stem cross-section, including sapwood, heartwood, and bark; height of plant and crown base, crown area and surface area; and the dry mass of leaf, stem, branches, sapwood, heartwood, bark, coarse roots and fine root tissues. We also report other properties of individuals (age, leaf size, leaf mass per area, wood density, nitrogen content of leaves and wood), as well as information about the growing environment (location, status, light, experimental treatment, vegetation type) where available. It is our hope that making these data available will improve our ability to understand plant growth, ecosystem dynamics, and carbon cycling in the worlds vegetation.

@@

```{r,results="asis",echo=FALSE, message=FALSE}
library(plyr)
library(whisker)
details2B  <-  daply(data, .(dataset), function(x)class2Bdetails(x))
writeLines(details2B,sep="\n\n")
```

>>>>

We (D. Falster and R. Duursma, with the help of D. Barneche, R. FitzJohn and A. Vårhammer) set out to create such a resource, by asking authors directly whether they would be willing to make their raw data files freely available. The response was overwhelming: nearly everyone we contacted was interested to contribute their raw data. Moreover, we were invited to incorporate another compilation led by M. Ishihara and focussing on Japanese literature. As a result, we present BAAD: a Biomass And Allometry Database for woody plants, comprising data collected in `r length(unique(data$studyName))` different published and unpublished studies.

@@

**2. Abstract**: Understanding how different plants are plant constructed -- i.e. how key size dimensions and the amount of mass invested in different tissues varies among individuals -- is essential for modelling plant growth, estimating carbon stocks, and mapping the flow of energy in the terrestrial biosphere. Allocation patterns can differ widely through ontogeny, but also among coexisting species, and among species adapted to or grown in different environments. While a variety of models dealing with allocation exist, a synthetic understanding about plant allocation is lacking. This is partly due to the lack of suitable datasets for validating and parametrising models. To that end, we present the Biomass And Allometry Database (BAAD) for woody plants. BAAD contains `r sum(!is.na(data[,vars]))` measurements collected in `r length(unique(data$studyName))` different studies, from `r nrow(data)` individuals across `r length(unique(data$species))` species. Most of this data is associated with an existing publication, however, mostly raw data files were not released at time of publication. Thus BAAD contains individual level data from different studies, transformed into standard units and variable names. The transformations were achieved using a new R package dataMashR.  Other features which distinguish BAAD are that we focussed on studies where: i) measurements were for individual plants rather than stand averages; ii) individuals spanning a range of sizes were measured; iii) inclusion of plants from 0.01-100m in height; and iii) biomass was estimated directly, i.e. not indirectly via allometric equations (with one exception for trees > 60m). We included both wild and artificially grown plants. The dataset contains the following size metrics: total leaf area; area of stem cross-section, including sapwood, heartwood, and bark; height of plant and crown base, crown area and surface area; and the dry mass of leaf, stem, branches, sapwood, heartwood, bark, coarse roots and fine root tissues. We also report other properties of individuals (age, leaf size, leaf mass per area, wood density, nitrogen content of leaves and wood), as well as information about the growing environment (location, status, light, experimental treatment, vegetation type) where available. It is our hope that making these data available will improve our ability to understand plant growth, ecosystem dynamics, and carbon cycling in the worlds vegetation.

@@

```{r,results="asis",echo=FALSE, message=FALSE}
library(plyr)
library(whisker)
details2B  <-  daply(data, .(studyName), function(x)class2Bdetails(x))
writeLines(details2B,sep="\n\n")
```
